Real Time Genome Scan Using GPU

### 2019-07-10 paper.tex
adding affiliations

\author[$\ast$]{Xiaoqi Hu}
\author[$\ast$]{Hyeonju Kim}
\author[$\ast$]{Saunak Sen}

\affil[$\ast$]{University of Tennessee Health Science Center}

>>>>

\author[$\ast$]{Xiaoqi Hu}
\author[$\ast$]{Hyeonju Kim}
\author[$\ast$]{GregoryFarage}
\author[$\dagger$]{PjotrPrins}
\author[$\dagger$]{RobertW.Williams}
\author[$\S$]{KarlW.Broman}
\author[$\ast$]{Saunak Sen}

\affil[$\ast$]{Department of Preventive Medicine, University of Tennessee Health Science Center, Memphis, TN} 
\affil[$\dagger$]{Department of Genetics, Genomics, and Informatics, University of Tennessee Health Science Center, Memphis, TN} 
\affil[$\S$]{Department of Biostatistics, University of Wisconsin-Madison, Madison, WI}
